### 2018-06-08 ident/docs/sifigures.tex
change external document
switched figures and added figure captions

\externaldocument{draft_2} % reference to existing external document

@@

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=0.6\textwidth,height=0.2\textheight, keepaspectratio]{figures/figure6/v1_v1max_ck_parameter_values}}
	\caption{}\label{fig:v1_v1max_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure1/v1_v1max_ck_ident_exp_info}}
	\caption{}\label{fig:v1_v1max_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure1/v3_ck_1_2_ident_exp_info}}
	\caption{}\label{fig:v3_1_ck_ident}
\end{figure}

>>>>

\externaldocument{draft_3} % reference to existing external document

@@

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/figure6/v1_kcat_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_kcat_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/figure6/v1_vmax_ck_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_v1max_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/figure1/v1_vmax_exp_info}}
	\caption{The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The percentage of total combinations of experimental data used for analysis (240 for $v_1$) that can identify each parameter is also specified. $v_1$ requires data from two experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $v_1$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second perturbation (green) required for identifying the parameters.}\label{fig:v1_v1max_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure1/v3_ck_exp_info}}
	\caption{a) The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_3$ when there is no noise in the input experimental data. The percentage of total combinations of experimental data used for analysis (3360) that can identify each parameter is also specified. $v_3$ required data from three experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $V_3^{max}$, c) $K_3^{fdp}$ and d) $K_3^{pep}$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second (green) and the third perturbation (yellow) required for identifying the parameters.}\label{fig:v3_1_ck_ident}
\end{figure}
